Introduction

### 2015-07-21 dissertation/problems.tex
other problems

>>>>

TODO: Paper yet to be done on caching.

\subsection{Future work; Discussion of other problems}

As noted in Section~\ref{sec:motivation} it is clear that evaluating
arbitrary SPARQL queries are in general unsustainable, and it is
likely that the problems in Section~\ref{sec:perfproblems} is partly
to blame for it. Our work, and most of the related work in
Section~\ref{sec:related} approach this work from the direction of
moving stress from the server, but it is also clear that another way
to address Problem~\ref{prob:sparqlcomplex} is for the SPARQL engine
to identify queries it would be too heavy to answer already when
parsing or planning, and also expose that in the service description
so that clients can avoid asking them. The HTTP/2 specification
\cite{rfc7540} has some generic facilities that may be helpful:

\begin{quote}
\texttt{ENHANCE\_YOUR\_CALM (0xb)}:  The endpoint detected that its peer is
      exhibiting a behavior that might be generating excessive load.
\end{quote}

% TODO: Discuss characteristic sets?

Problem~\ref{prob:queryeq} is best addressed by creating hashing
algorithms that have a reasonable chance of returning the same digest
if two queries are equivalent. Some works have created cryptographical
hashing functions, but they may be overly costly to compute for this
purpose. % TODO ref.
